---
title: "Homework 2"
author: "Robert George"
date: "9/23/2021"
output: github_document
---
###Homework 1
##Robert George

```{r cars}
library(tidyverse)
library(dplyr)
library(nycflights13)
library(ggplot2)
```

#How many flights have a missing dep_time?
```{r}
flights = flights
flights%>%
  summarize(sum(is.na(dep_time)))
```

#What other variables are missing? What might these rows represent?
```{r}
flights%>%
  filter(is.na(dep_time))
```
In rows where dep_time is missing, dep_delay, arr_time, arr_delay, and air_time are also missing. These rows represent cancelled flights.

#Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
library(lubridate)

lubri_flights = flights%>%
  mutate(dep_time =((dep_time %/% 100)*60) + (dep_time %% 100),
         sched_dep_time =  hour*60 + minute)
```

#Look at the number of canceled flights per day. Is there a pattern?

```{r}
flights%>%
  filter(is.na(dep_time))%>%
  group_by(month, day, year)%>%
  summarize(`canceled flights` = n(),
            date = make_date(year,month,day))%>%
  ggplot(aes(x = date, y = `canceled flights`))+
  geom_point()
```
There does not appear to be a pattern.Even if zoomed in by filtering out days with more than 100 missed flights, there does not seem to be any sort of pattern to the data.

#Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()

```{r}
flights%>%
  group_by(month, day, year)%>%
  summarize(date = make_date(year,month,day),
            canceled = sum(is.na(dep_time)),
            flights = n(),
            prop_canceled = sum(is.na(dep_time))/flights,
            avg_delay = ((mean(dep_delay, na.rm=TRUE)+mean(arr_delay, na.rm=TRUE))/2)/flights)%>%
  ggplot(aes(x = date))+
  geom_point(aes(y =prop_canceled, color = "proportion canceled"))+
  geom_point(aes(y = avg_delay, color = "avg delay per flight"))+
  geom_linerange(aes(x=date, ymin=prop_canceled, ymax=avg_delay, colour="difference"))
```
It seems that there is a slight affinity between the proportion of canceled flights per day and the average delay per flight per day. The difference lines indicate that at dates with large proportions of canceled flights, there tends to be greater delay per flight.
